Untitled

### 2021-01-29 ms/manuscript.Rmd
Switch to kableExtra for (most) tables

**Number of tables, black-and-white figures, and color figures.**  
No tables / 2 black-and-white figure / 1 color figure

@@

```{r pgls-stats}
sporo_vpd_pval <- env_range_dt_model_summary %>% filter(model == "sporo_vpd_model") %>% pull(p_value) %>%
  round_t(2)
gameto_vpd_pval <- env_range_dt_model_summary %>% filter(model == "gameto_vpd_model") %>% pull(p_value) %>%
  round_t(2)
```

Desiccation tolerance tended to increase with VPD for both gametophytes and sporophytes (Fig. 6).
These trends were significant when analyzed using PGLS for gametophytes (*P* = `r gameto_vpd_pval`) but not sporophytes (*P* = `r sporo_vpd_pval`; Appendix S5).

No significant relationship was detected between range size of gametophytes and DT.

@@

@@

```{r table-physig, results = "asis"}
# Format phylogenetic signal results as a pretty table
phylosig %>%
  mutate(k_pval_stars = case_when(
    k_pval < 0.001 ~ "***",
    k_pval < 0.01 ~ "**",
    k_pval < 0.05 ~ "*",
    TRUE ~ ""
  )) %>%
  mutate(lambda_pval_stars = case_when(
    lambda_pval < 0.001 ~ "***",
    lambda_pval < 0.01 ~ "**",
    lambda_pval < 0.05 ~ "*",
    TRUE ~ ""
  )) %>%
  mutate(
    kval = ifelse(kval < 0.001, format(kval, digits = 3), round_t(kval, 3)) %>% paste0(., k_pval_stars),
    lambda = ifelse(lambda < 0.001, format(lambda, digits = 3), round_t(lambda, 3)) %>% paste0(., lambda_pval_stars),
    trait = str_replace_all(trait, "recovery_mean", "Recovery") %>%
      str_replace_all("etr_mean", "ETR~max~") %>%
      str_replace_all("par_mean", "PPFD~95%~"),
    generation = str_to_sentence(generation)
  ) %>%
  select(generation, trait, kval, lambda) %>%
  group_by(generation) %>%
  gt(rowname_col = "species") %>%
  cols_label(kval = md("*K*"), lambda = "λ", trait = "") %>%
  as_latex()
```

@@

```{r glmm-summary, results = "asis"}
# Format GLMM summary for printing
glmm_summary %>%
  mutate(
    fixed_effects = case_when(
      fixed_effects == "both" ~ "Generation + habit",
      fixed_effects == "intersect" ~ "Generation + habit + Generation:habit",
      TRUE ~ str_to_sentence(fixed_effects)
    ),
    response = str_replace_all(response, "recovery", "Recovery") %>%
      str_replace_all("etr", "ETR~max~") %>%
      str_replace_all("par", "PPFD~95%~")
  ) %>%
  group_by(response) %>%
  gt() %>%
  cols_label(
    fixed_effects = "Fixed effects", 
    response = "Response", 
    delta_DIC = "delta DIC") %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(
      columns = everything(),
      rows = delta_DIC == 0)) %>%
  fmt_number(
    columns = vars(DIC, delta_DIC)
  ) %>%
  as_latex()
```

@@

```{r glmm-table-kableextra, results = "asis"}
group_locs <-
glmm_summary %>% mutate(row_num = 1:nrow(.)) %>% group_by(response) %>%
  summarize(
    start = min(row_num),
    end = max(row_num),
    .groups = "drop"
  )

glmm_summary %>%
  mutate(
    fixed_effects = case_when(
      fixed_effects == "both" ~ "Generation + habit",
      fixed_effects == "intersect" ~ "Generation + habit + Generation:habit",
      TRUE ~ str_to_sentence(fixed_effects)
    ),
    response = str_replace_all(response, "recovery", "Recovery") %>%
      str_replace_all("etr", "ETR~max~") %>%
      str_replace_all("par", "PPFD~95%~"),
    DIC = round_t(DIC, 2),
    delta_DIC = round_t(delta_DIC, 2)
  ) %>%
  select(fixed_effects, response, DIC, delta_DIC) %>%
  kbl(format = "latex", booktabs = TRUE, col.names = c("Fixed effects", "Response", "DIC", "delta DIC")) %>%
  row_spec(which(glmm_summary$delta_DIC == 0), bold = TRUE) %>%
  pack_rows(
    "ETR\\textsubscript{max}", 
    group_locs %>% filter(response == "etr") %>% pull(start),
    group_locs %>% filter(response == "etr") %>% pull(end),
    escape = FALSE)
```

@@

```{r glmm-params, results = "asis"}
# Format summary of best GLMM parameters for printing
glmm_params %>%
  mutate(
    fixed_effects = str_to_sentence(fixed_effects),
    response = str_replace_all(response, "recovery", "Recovery") %>%
      str_replace_all("etr", "ETR~max~") %>%
      str_replace_all("par", "PPFD~95%~"),
    predictor = str_replace_all(predictor, "generationsporophyte", "Sporophyte") %>%
      str_replace_all("habitLow_Epiphyte", "Low Epiphyte") %>%
      str_replace_all("habitSaxicolous", "Saxicolous") %>%
      str_replace_all("habitTerrestrial", "Terrestrial")
  ) %>%
  group_by(response) %>%
  gt() %>%
  cols_label(
    fixed_effects = "Fixed effects", 
    predictor = "Predictor", 
    post.mean = "Mean effect",
    `l-95% CI` = "Lower 95% CI",
    `u-95% CI` = "Upper 95% CI",
    eff.samp = "Ef. sample size",
    pMCMC = md("*P* MCMC")) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(
      columns = everything(),
      rows = pMCMC < 0.05)) %>%
  fmt_number(columns = vars(post.mean, `l-95% CI`, `u-95% CI`)) %>%
  fmt_number(columns = vars(eff.samp), decimals = 0) %>%
  fmt_number(columns = vars(pMCMC), decimals = 3, drop_trailing_zeros = TRUE) %>%
as_latex()
```

@@

**`r table("pglm")`** Phylogenetic generalized least squares (PLGS) models of desiccation tolerance as a function of environmental water potential (VPD) or the range of gametophytes beyond sporophytes (G beyond S) in filmy ferns from Moorea, French Polynesia

```{r pglm, results = "asis"}
env_range_dt_model_summary %>%
  mutate(generation = case_when(
    str_detect(model, "sporo") ~ "S",
    str_detect(model, "gameto") ~ "G"
  )) %>%
  assert(not_na, generation) %>%
  mutate(
    predictor = case_when(
      str_detect(model, "vpd") ~ "VPD",
      str_detect(model, "range") ~ "G beyond S"
    )
  ) %>%
  assert(not_na, predictor) %>%
  select(generation, predictor, df, f_value, adj_r_squared, p_value) %>%
  mutate(
    f_value = round_t(f_value, 3),
    p_value = round_t(p_value, 3),
    adj_r_squared = round_t(adj_r_squared, 3)
  ) %>%
  kbl(col.names = c("Generation", "Predictor", "df", "$F$", "adj. $R^2$", "$P$"), escape = FALSE, booktabs = TRUE)
```

>>>>

**Number of tables, black-and-white figures, and color figures.**  
4 tables / 0 black-and-white figures / 4 color figures

@@

```{r pgls-stats}
sporo_vpd_pval <- env_range_dt_model_summary %>% filter(model == "sporo_vpd_model") %>% pull(p_value) %>%
  round_t(3)
gameto_vpd_pval <- env_range_dt_model_summary %>% filter(model == "gameto_vpd_model") %>% pull(p_value) %>%
  round_t(3)
```

Desiccation tolerance tended to increase with VPD for sporophytes, but not gametophytes (`r figure("corr")`).
These trends were marginally non-significant when analyzed using PGLS for sporophytes (*P* = `r sporo_vpd_pval`) and not significant for gametophytes (*P* = `r gameto_vpd_pval`; `r table("pgls")`).

No significant relationship was detected between range size of gametophytes and DT (`r figure("corr")`, `r table("pgls")`).

@@

```{r table-setup}
options(knitr.table.format = "latex")
```

@@

```{r physig-table, results = "asis"}
# Format phylogenetic signal results as a pretty table with kableExtra

# Make helper table for formatting by groups
phylosig_group_locs <-
phylosig %>% mutate(row_num = 1:nrow(.)) %>% group_by(generation) %>%
  summarize(
    start = min(row_num),
    end = max(row_num),
    .groups = "drop"
  )

phylosig %>%
  mutate(k_pval_stars = case_when(
    k_pval < 0.001 ~ "***",
    k_pval < 0.01 ~ "**",
    k_pval < 0.05 ~ "*",
    TRUE ~ ""
  )) %>%
  mutate(lambda_pval_stars = case_when(
    lambda_pval < 0.001 ~ "***",
    lambda_pval < 0.01 ~ "**",
    lambda_pval < 0.05 ~ "*",
    TRUE ~ ""
  )) %>%
  mutate(
    kval = ifelse(kval < 0.001, format(kval, digits = 3), round_t(kval, 3)) %>% paste0(., k_pval_stars),
    lambda = ifelse(lambda < 0.001, format(lambda, digits = 3), round_t(lambda, 3)) %>% paste0(., lambda_pval_stars),
    trait = str_replace_all(trait, "recovery_mean", "Recovery") %>%
      str_replace_all("etr_mean", "ETR\\\\textsubscript{max}") %>%
      str_replace_all("par_mean", "PPFD\\\\textsubscript{95\\\\%}"),
    generation = str_to_sentence(generation)
  ) %>%
  select(trait, kval, lambda) %>%
  kbl(format = "latex", booktabs = TRUE, col.names = c("", "\\textit{K}", "λ"), escape = FALSE) %>%
  pack_rows(
    "Sporophytes", 
    phylosig_group_locs %>% filter(generation == "sporophyte") %>% pull(start),
    phylosig_group_locs %>% filter(generation == "sporophyte") %>% pull(end),
    escape = FALSE) %>%
  pack_rows(
    "Gametophytes", 
    phylosig_group_locs %>% filter(generation == "gametophyte") %>% pull(start),
    phylosig_group_locs %>% filter(generation == "gametophyte") %>% pull(end),
    escape = FALSE)
```

@@

```{r glmm-table, results = "asis"}
glmm_summ_group_locs <-
glmm_summary %>% mutate(row_num = 1:nrow(.)) %>% group_by(response) %>%
  summarize(
    start = min(row_num),
    end = max(row_num),
    .groups = "drop"
  )

glmm_summary %>%
  mutate(
    fixed_effects = case_when(
      fixed_effects == "both" ~ "Generation + habit",
      fixed_effects == "intersect" ~ "Generation + habit + Generation:habit",
      TRUE ~ str_to_sentence(fixed_effects)
    ),
    DIC = round_t(DIC, 2),
    delta_DIC = round_t(delta_DIC, 2)
  ) %>%
  select(fixed_effects, DIC, delta_DIC) %>%
  kbl(format = "latex", booktabs = TRUE, col.names = c("Fixed effects", "DIC", "delta DIC"), escape = TRUE) %>%
  row_spec(which(glmm_summary$delta_DIC == 0), bold = TRUE) %>%
  pack_rows(
    "ETR\\\\textsubscript{max}", 
    glmm_summ_group_locs %>% filter(response == "etr") %>% pull(start),
    glmm_summ_group_locs %>% filter(response == "etr") %>% pull(end),
    escape = FALSE) %>%
  pack_rows(
    "PPFD\\\\textsubscript{95\\\\%}", 
    glmm_summ_group_locs %>% filter(response == "par") %>% pull(start),
    glmm_summ_group_locs %>% filter(response == "par") %>% pull(end),
    escape = FALSE) %>%
  pack_rows(
    "Recovery", 
    glmm_summ_group_locs %>% filter(response == "recovery") %>% pull(start),
    glmm_summ_group_locs %>% filter(response == "recovery") %>% pull(end),
    escape = FALSE)
```

@@

@@

```{r glmm-params, results = "asis"}
# Make helper table for formatting by groups
glmm_params_group_locs <-
glmm_params %>% mutate(row_num = 1:nrow(.)) %>% group_by(response) %>%
  summarize(
    start = min(row_num),
    end = max(row_num),
    .groups = "drop"
  )

glmm_params_cols <-
  c(
    "Fixed effects" = "fixed_effects", 
    "Predictor" = "predictor",
    "Mean effect" = "post.mean",
    "Lower 95\\% CI" = "l-95% CI",
    "Upper 95\\% CI" = "u-95% CI",
    "Ef. sample size" = "eff.samp",
    "\\textit{P} MCMC" = "pMCMC"
  )

glmm_params %>%
  mutate(
    fixed_effects = str_to_sentence(fixed_effects),
    predictor = str_replace_all(predictor, "generationsporophyte", "Sporophyte") %>%
      str_replace_all("habitLow_Epiphyte", "Low Epiphyte") %>%
      str_replace_all("habitSaxicolous", "Saxicolous") %>%
      str_replace_all("habitTerrestrial", "Terrestrial")
  ) %>%
  select(all_of(glmm_params_cols)) %>%
  kbl(format = "latex", booktabs = TRUE, escape = FALSE) %>%
  kable_styling(latex_options = "scale_down") %>%
  row_spec(which(glmm_params$pMCMC < 0.05), bold = TRUE) %>%
  pack_rows(
    "ETR\\\\textsubscript{max}", 
    glmm_params_group_locs %>% filter(response == "etr") %>% pull(start),
    glmm_params_group_locs %>% filter(response == "etr") %>% pull(end),
    escape = FALSE) %>%
  pack_rows(
    "PPFD\\\\textsubscript{95\\\\%}", 
    glmm_params_group_locs %>% filter(response == "par") %>% pull(start),
    glmm_params_group_locs %>% filter(response == "par") %>% pull(end),
    escape = FALSE) %>%
  pack_rows(
    "Recovery", 
    glmm_params_group_locs %>% filter(response == "recovery") %>% pull(start),
    glmm_params_group_locs %>% filter(response == "recovery") %>% pull(end),
    escape = FALSE)
```

@@

**`r table("pgls")`** Phylogenetic generalized least squares (PLGS) models of desiccation tolerance as a function of environmental water potential (VPD) or the range of gametophytes beyond sporophytes (G beyond S) in filmy ferns from Moorea, French Polynesia

```{r pgls, results = "asis"}
env_range_dt_model_summary %>%
  mutate(generation = case_when(
    str_detect(model, "sporo") ~ "S",
    str_detect(model, "gameto") ~ "G"
  )) %>%
  assert(not_na, generation) %>%
  mutate(
    predictor = case_when(
      str_detect(model, "vpd") ~ "VPD",
      str_detect(model, "range") ~ "G beyond S"
    )
  ) %>%
  assert(not_na, predictor) %>%
  select(generation, predictor, df, f_value, adj_r_squared, p_value) %>%
  mutate(
    f_value = round_t(f_value, 3),
    p_value = round_t(p_value, 3),
    adj_r_squared = round_t(adj_r_squared, 3)
  ) %>%
  kbl(col.names = c("Generation", "Predictor", "df", "$F$", "adj. $R^2$", "$P$"), escape = FALSE, booktabs = TRUE)
```
